\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage{enumitem}

% Formatting
\titleformat{\section}{\large\bfseries\uppercase}{}{0em}{}[\titlerule]
\titlespacing*{\section}{0pt}{10pt}{5pt}

\begin{document}

% Header
\begin{center}
    {\Huge \textbf{John Doe}} \\
    \vspace{2mm}
    Political AI Consultant $\cdot$ Computational Aesthete $\cdot$ Memetic Engineer \\
    \vspace{1mm}
    \href{mailto:john.doe@yeezy.com}{john.doe@yeezy.com} $\cdot$ +1 (312) 555-0199 $\cdot$ Cody, Wyoming
\end{center}

% Experience
\section{Professional Experience}

\textbf{YE2024 Campaign} \hfill \textit{Remote / Cody, WY} \\
\textit{Chief AI Strategist} \hfill \textit{Nov 2022 -- Present}
\begin{itemize}[leftmargin=*]
    \item Architected the ``Donda-OS'' neural network, a proprietary LLM fine-tuned on 808s \& Heartbreak lyrics to generate policy proposals with high emotional resonance.
    \item Deployed autonomous agents to analyze Twitter/X sentiment, achieving a 400\% increase in viral engagement through algorithmic controversy optimization.
    \item Managed a team of 12 prompt engineers to synthesize campaign visuals using Stable Diffusion, establishing a distinct ``brutalist-futurist'' aesthetic.
\end{itemize}

\textbf{Yeezy Supply} \hfill \textit{Calabasas, CA} \\
\textit{Head of Digital Sovereignty} \hfill \textit{Jun 2019 -- Oct 2022}
\begin{itemize}[leftmargin=*]
    \item Led the migration of the entire supply chain to a private blockchain, ensuring 100\% transparency and zero reliance on ``traditional'' logistics providers.
    \item Developed ``YZY-SHLD'', a bot-mitigation system that used behavioral biometrics to prioritize true fans during limited sneaker drops.
\end{itemize}

\textbf{Gap Inc.} \hfill \textit{San Francisco, CA} \\
\textit{Strategic Visionary (Contract)} \hfill \textit{Jan 2018 -- May 2019}
\begin{itemize}[leftmargin=*]
    \item Consulted on the ``Perfect Hoodie'' project, utilizing computer vision to analyze 10,000 hours of archival footage to determine the mathematically perfect hood drape.
\end{itemize}

% Education
\section{Education}

\textbf{University of Chicago} \hfill \textit{Chicago, IL} \\
\textit{PhD in Computational Aesthetics} \hfill \textit{2018} \\
Thesis: \textit{``The Life of Pablo as a Stochastic Process: Markov Chains in Modern Hip-Hop''}

\textbf{MIT Media Lab} \hfill \textit{Cambridge, MA} \\
\textit{BS in Media Arts \& Sciences} \hfill \textit{2014}

% Skills
\section{Skills}
\begin{itemize}[leftmargin=*]
    \item \textbf{AI/ML:} PyTorch, TensorFlow, Hugging Face Transformers, Large Language Model Fine-tuning (LoRA/QLoRA).
    \item \textbf{Languages:} Python, Rust, Solidity, Latin (Intermediate).
    \item \textbf{Tools:} Docker, Kubernetes, Qdrant, Ableton Live.
    \item \textbf{Soft Skills:} Radical Candor, Visionary Thinking, Chaos Management.
\end{itemize}

\end{document}
